### 2017-10-22 paper/sexSelectionSpacingAppendix-ver1.tex
Change from quarters to months

\begin{figure}[htpb!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=4,518)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,309)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,762)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=25,486)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=23,360)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,922)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with no education by quarter (3 month
period). 
Predictions based on age 16 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_low}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=3,666)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,104)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,302)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=7,496)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=9,000)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=5,208)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
period). 
Predictions based on age 17 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_med}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=7,338)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=11,045)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=9,116)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=3,933)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=8,027)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,504)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 8 or more years of education by quarter
(3 month period). 
Predictions based on age 20 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_high}
\end{figure}

@@

% SPELL 2 - URBAN - LOW
\begin{figure}[h]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=1,596)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=2,232)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=952)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=1,754)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=2,411)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=930)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_urban}
\end{figure}

>>>>

\begin{figure}[htpb!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=4,518)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,309)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,762)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=25,486)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=23,360)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,922)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with no education by month beginning at marriage. 
Predictions based on age 16 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_low}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=3,666)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,104)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,302)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=7,496)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=9,000)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=5,208)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 1 to 7 years of education by month beginning at marriage. 
Predictions based on age 17 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_med}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=7,338)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=11,045)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=9,116)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=3,933)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=8,027)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,504)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 8 or more years of education by month beginning at marriage. 
Predictions based on age 20 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_high}
\end{figure}

@@

% SPELL 2 - URBAN - LOW
\begin{figure}[h]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=1,596)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=2,232)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=952)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=1,754)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=2,411)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=930)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with no education by month beginning 9 months after prior birth. 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_urban}
\end{figure}

% SPELL 2 - rural - LOW
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=8,426)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=11,481)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=3,686)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=9,395)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=12,127)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=3,860)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with no education by month beginning 9 months after prior birth. 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_rural}
\end{figure}
